Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-22 doc/JFLA2022/paper.tex
small corrections

\institute{
Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France \\
  \email{pierre.casteran@labri.fr}
\and
   Ask for agreement !
 }

@@

\section{Changes in the library}
The 2018 article contains the proof of  a variant of Theorem~\ref{kp:thm2}:

@@

We prove now that Theorem~\ref{thm3} still holds with this ``usual'' kind of battles, by borrowing new combinatorial results from~\cite{KS81}.

 Without loss of generality, we could consider the following restrictions:

@@

Let $\alpha<\epsilon_0$ be an ordinal.
Using the \texttt{coq-equations} plug-in~\cite{sozeau:hal-01671777}, we define the function which returns the number of steps of the battle starting with $\alpha$ at step $i$ for  any $i\in\mathbb{N}$.
We prove that this number is greater or equal than
$H'_\alpha(i)-i$, where $H'$ is a slight variant of the Wainer Hardy hierarchy of rapidly growing functions~\cite{BW85, KS81, Promel2013, Wainer1970}, defined by transfinite recursion in Fig.~\ref{fig:Hprime}.

@@

\label{sect:not-pr}
From this result, we infer that the considered function is not primitive recursive in general (for $\alpha\geq\omega^\omega$).

>>>>

\institute{
Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France \\
  \email{pierre.casteran@labri.fr}
\and
   to fill!
 }

@@

\section{Changes in the library}
The 2018 article contains a formal proof of  a variant of Theorem~\ref{kp:thm2}:

@@

We prove now that Theorem~\ref{thm3} still holds with this ``usual'' kind of battles, by borrowing new combinatorial results from~\cite{KS81}.
Without loss of generality, we could consider the following restrictions:

@@

Let $\alpha<\epsilon_0$ be an ordinal.
Using the \texttt{coq-equations} plug-in~\cite{sozeau:hal-01671777}, we define the function which returns the number of steps of the battle starting with $\alpha$ at step $i$ for  any $i\in\mathbb{N}$.
We prove that this number is greater or equal than
$H'_\alpha(i)-i$, where $H'$ is a slight variant of the Wainer Hardy hierarchy of rapidly growing functions~\cite{BW85, KS81, Promel2013, Wainer1970}, defined by transfinite recursion in Fig.~\ref{fig:Hprime}.
From this result, we infer that the considered function is not primitive recursive in general (for $\alpha\geq\omega^\omega$).

@@

\label{sect:not-pr}
